### 2020-06-30 introduction.tex
intro_cl_063016pm

% introduce LPL asynchronous duty cycle media access
As already we are aware, smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing". 
Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes. And studies show that a great portion of these attacks are casual and opportunistic without technical equipment~\cite{eiband2017understanding}, say a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password without knowing the account for critical apps like Alipay, which seldom appears on screen in common usages. 
% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

The privacy threat however has been exacerbated with the rapidly developed mobile camera module these years. Given the commercial smartphone, the attacker cannot acquire sensitive information from a long distance to reduce suspicion, but also recognize the information accurately for propagating, making existing defense work ineffective. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second. And more images mean more recorded information of the victim. To gain vital data stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.

@@

To mitigate this threat, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm. \cl{supplement elements for long range, blurred input and the recognized results.}}
	\label{illustration_of_system}
\end{figure}

@@

  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without much room for focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally" captured photos (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, images we face exhibit lower concentrations of information and more artifacts, and needs reliable ``reconstruction" than ``interpolation"". Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character. 

@@

  On one hand, each photo is blurred with a randomly different PSF kernel, which, because of the extreme blurriness, cannot be approximated as a constant, isotropic gaussian kernel. Thus they cannot be processed as a video clip due to the lacking consistency between neighboring frames\cl{citation?}, shown in Figure~\ref{illustration_of_system}; on the other hand, because of the low concentration of information, blurred photos are similar to pieces of a jigsaw puzzle, each containing only fractions of information.

@@

  Few useful information can be extracted separately and merged directly to produce satisfactory results if processed by common procedures to enhance the resolution of a series of snapshots\cl{citation?}. 
  \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents. However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred photos as input. Since smartphones can capture 10 snapshots per second in burst mode. Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cl{citation?}. The reason has two folds. First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment. Second, the nature of our task requires to do pixel-wise correlation and comparison with same coordinates on consecutive images throughout our construction process. Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this photo.

@@

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}
Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings. The system is able to capture photos and produce high-res images constantly with about 2 seconds interval. Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.

>>>>

% introduce LPL asynchronous duty cycle media access
Smartphones have become a necessity in our lives, as we are checking our mobile phones constantly throughout the day. As a result, some privacy concerns have arisen about nearby parties peeking at our screen, namely ``shoulder surfing". 
Given that the attacker is not malicious and merely takes several peeks out of curiosity, most works in this area are built on a threat model of an attacker observing with naked eyes, avoiding the severe data leakage effectively~\cite{eiband2017understanding}. For example, a mere stranger can hardly do any harm reading a fragment of the correspondence or acquiring the password shown on screen without any equipment. 
% It is however the rare but malicious attacker, with certain familiarity and knowledge of the victim, that can do the most harm. The attacker can even be our closest friends or family members, as there are various cases in China where a child obtains Alipay password of their parents and is unaware that electronic payments consists of 'real' money, resulting in spending them lavishly in their games. Besides, specially designed equipment are not a necessity for the shoulder surfing attack.

The privacy threat however has been exacerbated with the rapidly developed mobile camera module these years. Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second. And more images mean more recorded information of the victim. Given the commercial smartphone, the attacker can record the information reliably for propagating. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. To gain vital data more stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.

@@

Unfortunately, none of existing work can mitigate the new threat model. Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it's imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/intro.png}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm. \cl{supplement elements for long range, blurred input and the recognized results.}}
	\label{illustration_of_system}
\end{figure}

@@

  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally" captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction" than ``interpolation". Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character. 

@@

  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames\cl{citation?}, shown in Figure~\ref{illustration_of_system}. Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle.

@@

  Few useful information can be extracted separately and merged directly to produce perceptible results if processed by common procedures to enhance the resolution of blurred snapshots\cl{citation?}. 
  \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents. However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred snapshots as input. Since smartphones can capture 10 snapshots per second in burst mode. Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cl{citation?}. The reason has two folds. First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment. Second, the nature of our task requires to do pixel-wise correlation and comparison with same coordinates on consecutive images throughout our construction process. Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this snapshot.

@@

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}
Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings. The system is able to capture snapshots and produce high-res images constantly with about 2 seconds interval. Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.
